---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
library(ramp.control)
attach(yaml::read_yaml("../../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 #load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
eir_files <- list.files(path = directory, pattern = "*_Lambda_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(Lambda_files[i])
  fitted_mod[[i]]$nHostSpecies <- 1
fitted_mod[[i]]$nVectorSpecies <- 1

}
valsf <- get_XH(fitted_mod[[2]])
with(valsf, plot(fitted_mod[[2]]$outputs$time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data_list[[2]]$district_name), type = "l", ylim = c(0,1), col="darkred"))
  #with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data_list[[2]], lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  add_irs_history(unique(data_list[[1]]$district_name))
```


 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){
mod_file <- model_list[[i]]
data <- data_list[[i]]

cf_max <- make_cf_base_max(ix, mod_file)
  cf_min <- make_cf_base_min(ix, mod_file)
  cf_median <- make_cf_base_median(ix, mod_file)
  cf_mean <- make_cf_base_mean(ix, mod_file)
  mod1a <- modify_baseline(mod_file, cf_max) 
  mod1b <- modify_baseline(mod_file, cf_min) 
  mod1c <- modify_baseline(mod_file, cf_median) 
  mod1d <- modify_baseline(mod_file, cf_mean) 
  mod1a <- setup_other_variables(mod1a)
  vals <- get_XH(mod_file)
  vals1a <- get_XH(mod1a)
  vals1b <- get_XH(mod1b)
  vals1c <- get_XH(mod1c)
  vals1d <- get_XH(mod1d)


mod_for_cast <- last_to_inits(mod_file)
mod_for_cast$nHostSpecies <- 1
mod_for_cast$nVectorSpecies <- 1
mod_for_cast <- setup_other_variables(mod_for_cast)
mod_for_cast <- forecast_spline_Lambda(mod_for_cast, 5, x_last = 1)
tt <- seq(0, ceiling(max(data$jdate) / 365) * 365 + (5 * 365), length.out = 200)

mod_for_cast <- xds_solve(mod_for_cast, Tmax = max(tt))

vals_for <- get_XH(mod_for_cast)
time_years <- mod_for_cast$outputs$time / 365 + FirstYear
t <- time_years

#base_mod <- model_list[[i]]  # Reset base model for each iteration
coverage <- c(0.3, 0.5, 0.8, 1)
par(mfrow = c(2, 2), mar = c(4, 4, 3, 1), oma = c(0, 0, 2, 0))

for (c in coverage) {
  #ITN
  itn_effect <- 0.9
  itn_start <- itn_effect*c
  itn_end <- 0.01
  decay_start <- 2023
  decay_end <- 2026
  t0 <- (decay_start + decay_end) / 2
  k <- 0.1
```


```{r, fig.height=8, fig.width=11}
#IRS
  irs_effect <- 0.8
  irs_start <- itn_effect*c
  irs_end <- 0.01
  decay_start_irs <- 2024
  decay_end_irs <- 2025
  t0 <- (decay_start_irs + decay_end_irs) / 2
  k_irs <- 0.5
```


```{r, fig.height=8, fig.width=11}
effect_decay <- function(t, e0, e1, k_eff, t0_eff) {
    e1 + (e0 - e1) / (1 + exp(k_eff * (t - t0_eff)))
  }

 logistic_pr_with_effect_decay <- function(t, pr0, e0, e1, k_eff, t0_eff, k_pr, t0_pr) {
    effect_t <- effect_decay(t, e0, e1, k_eff, t0_eff)
    pr0 * (1 - (effect_t / (1 + exp(-k_pr * (t - t0_pr)))))
  }

  pr_itn <- logistic_pr_with_effect_decay(time_years, vals_for$true_pr, effect_itn_start, effect_itn_end, k, t0, k, t0)
  pr_itn_2026 <- logistic_pr_with_effect_decay(time_years, pr_itn, effect_itn_start, effect_itn_end, k, t01, k, t01)
  
  pr_irs <- logistic_pr_with_effect_decay(time_years, vals_for$true_pr, effect_itn_start, effect_itn_end, k, t0, k, t0)
  pr_irs_2025 <- logistic_pr_with_effect_decay(time_years, pr_irs, effect_irs_start, effect_irs_end, k, t01, k, t01)


  
  df <- data.frame(
    Year = time_years,
    Original_PR = vals_for$true_pr,
    itn_PR = round(pr_itn, 4),
    itn_PR_2026 = round(pr_itn_2026, 4)
  )
  df <- df[df$Year >= 2020,]

  plot(df$Year, df$Original_PR, type = "l", lwd = 2, col = "blue",
       ylim = c(0, 1), ylab = "Parasite Rate (PR)", xlab = "Year",
       main = paste(unique(data$district_name), "-", "cov=", c * 100, "%"))

  lines(df$Year, df$itn_PR, col = "darkred", lwd = 2)
  lines(df$Year, df$itn_PR_2026, col = "green", lwd = 2)
  with(data, lines(jdate / 365 + FirstYear, pfpr, type = "o", col = "darkblue"))
}

}
```

```{r}
#pdf("itn_scenario_time_decay_cov.pdf")
#for(i in 1:length(itn_time))
for(i in 4)
  profile_itn(i, fitted_mod, data_list)
#dev.off(dev.cur())
```
