---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
library(ramp.control)
attach(yaml::read_yaml("../../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
# #load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
Lambda_files <- list.files(path = directory, pattern = "*_eir_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(Lambda_files[i])
  fitted_mod[[i]]$nHostSpecies <- 1
fitted_mod[[i]]$nVectorSpecies <- 1

}
valsf <- get_XH(fitted_mod[[3]])
with(valsf, plot(fitted_mod[[3]]$outputs$time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data_list[[3]]$district_name), type = "l", ylim = c(0,1), col="darkred"))
  #with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data_list[[3]], lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  add_itn_history(unique(data_list[[3]]$district_name))
```


 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){

mod_file <- fitted_mod[[1]]#model_list[[i]]
data <- data_list[[1]]

mod_for_cast <- last_to_inits(mod_file)
mod_for_cast$nHostSpecies <- 1
mod_for_cast$nVectorSpecies <- 1
mod_for_cast <- setup_other_variables(mod_for_cast)
mod_for_cast <- forecast_spline_EIR(mod_for_cast, 5, x_last = 1)
tt <- seq(0, ceiling(max(data$jdate) / 365) * 365 + (5 * 365), length.out = 200)
#- xds_solve_cohort(mod, times=tt)
mod_for_cast <- xds_solve_cohort(mod_for_cast, times=tt)

vals_for <- get_XH(mod_for_cast)
time_years <- mod_for_cast$outputs$time / 365 + FirstYear
t <- time_years

itn_mod <- last_to_inits(mod_for_cast)

F_season = function(t)
    {ifelse(t < 0, 0, (sin(2*pi*(t-365/4) / 365) + 1))}
cover_par <- list(trend_par = makepar_F_sharkfin())
itn_mod <- setup_bednets(itn_mod, 
                         coverage_name = "func", 
                         coverage_opts = cover_par, 
                         effectsizes_name = "lemenach")
mod_for_cast_cov <- xds_solve_cohort(itn_mod, times = tt)
vals_cov <- get_XH(mod_for_cast_cov)

  df <- data.frame(
    Year = t,
    Original_PR = round(vals_for$true_pr,4),
    itn_PR = round(vals_cov$true_pr, 4)
  )
  df <- df[df$Year >= 2020,]

  plot(df$Year, df$Original_PR, type = "l", lwd = 2, col = "blue",
       ylim = c(0, 1), ylab = "Parasite Rate (PR)", xlab = "Year",
       main = paste(unique(data$district_name), "-"))

  lines(df$Year, df$itn_PR, col = "darkred", lwd = 2)
  with(data, lines(jdate / 365 + FirstYear, pfpr, type = "o", pch= 16,col = "darkblue"))


}
```

```{r}
for(i in 1)
  profile_itn(i, fitted_mod, data_list)
```
