---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
library(ramp.control)
attach(yaml::read_yaml("../../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
# #load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
eir_files <- list.files(path = directory, pattern = "*_Lambda_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(eir_files[i])
  fitted_mod[[i]]$nHostSpecies <- 1
fitted_mod[[i]]$nVectorSpecies <- 1

}
valsf <- get_XH(fitted_mod[[2]])
with(valsf, plot(fitted_mod[[2]]$outputs$time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data_list[[2]]$district_name), type = "l", ylim = c(0,1), col="darkred"))
  #with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data_list[[2]], lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  add_irs_history(unique(data_list[[1]]$district_name))
```

```{r}
percent_eff <- read.csv(file="C:/Users/Admin/Box/RAMP/data/effect_sizes/ITN/malaria_type_itn_eff_2023.csv")
percent_eff$mean_percent[percent_eff$mean_percent < 0] <- 0

```

mean effect by ITN type
```{r}
itn_file_only <- read.csv(file ="C:/Users/Admin/Box/RAMP/data/effect_sizes/ITN/only_itn_eff.csv")
average_eff <- aggregate(mean_percent ~ ITN_Type, data = itn_file_only, FUN = mean)
```


 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){
  mod_file <- fitted_mod[[2]]#model_list[[i]]
  data <- data_list[[2]]

   ##--------------------------------------------------------------------------------------------------
  mod_for_cast <- last_to_inits(mod_file)
  mod_for_cast<- forecast_spline_Lambda(mod_for_cast, 5,x_last=1)
  tt <- seq(0,ceiling(max(data$jdate)/365)*365+(5*365) ,length.out=200)
  mod_for_cast <- setup_other_variables(mod_for_cast) 
   mod_for_cast <- xds_solve(mod_for_cast, Tmax =365 )

  ## Get outputs for the diffferent models
  vals_for <- get_XH(mod_for_cast)

 # Time cutoff for effect to start
  vals_for <- as.data.frame(vals_for)
   time_years <- vals_for$time/365+FirstYear
 # Set layout to 2x2 grid
par(mfrow = c(2, 2), mar = c(4, 4, 3, 1), oma = c(0, 0, 2, 0))  # Outer margin at top for legend

mod_file <- last_to_inits(mod_file)

 cov_opts <- list(
  mean = 0.5, 
  F_season = function(t)
  {ifelse(t < 0, 0, (sin(2*pi*(t-365/4) / 365) + 1))}
)
 #  cov_opts <- list(
 # F_season =  function(t, e0, e1, k_eff, t0_eff) {
  #  e1 + (e0 - e1) / (1 + exp(k_eff * (t - t0_eff)))
  #})

mod_file<- setup_other_variables(mod_file) 
itn_mod <- setup_bednets(mod_file,
     coverage_name = "func", coverage_opts = cov_opts, 
     effectsizes_name = "lemenach")

xds_solve(itn_mod, 1830, dt=15) -> itn_mod
  
  vals_cov <- get_XH(itn_mod)

  df <- data.frame(
    Year = time_years,
    Original_PR = vals_for$true_pr,
    itn_PR = round(vals_cov$true_pr, 4),
    #itn_PR_2026 = round(pr_itn_2026, 4)
  )
  df <- df[df$Year >= 2020,]
  df_first <- df[df$Year >= 2023 & df$Year <= 2026, ]
  df_sec   <- df[df$Year >= 2025.8, ]

  # === Plot for each ITN type ===
  plot(df$Year, df$Original_PR, type = "l", lwd = 2, col = "blue",
       ylim = c(0, 1),
       ylab = "Parasite Rate (PR)", xlab = "Year",
       main = paste(unique(data$district_name), "-", "cov=", j*100,"%"))

  lines(df$Year, df$itn_PR, col = "darkred", lwd = 2)
  #lines(df$Year, df$itn_PR_2026, col = "green", lwd = 2)
  with(data, lines(jdate / 365 + FirstYear, pfpr, pch = 16, type = "o", col = "darkblue"))

}

}
```

```{r}
#pdf("itn_scenario_time_decay_cov.pdf")
#for(i in 1:length(itn_time))
for(i in 1)
  profile_itn(i, fitted_mod, data_list)
#dev.off(dev.cur())
```
