---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
library(ramp.control)
attach(yaml::read_yaml("../../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
# #load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
eir_files <- list.files(path = directory, pattern = "*_Lambda_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(eir_files[i])
  fitted_mod[[i]]$nHostSpecies <- 1
fitted_mod[[i]]$nVectorSpecies <- 1

}
valsf <- get_XH(fitted_mod[[2]])
with(valsf, plot(fitted_mod[[2]]$outputs$time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data_list[[2]]$district_name), type = "l", ylim = c(0,1), col="darkred"))
  #with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data_list[[2]], lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  add_irs_history(unique(data_list[[1]]$district_name))
```


 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){
mod_file <- model_list[[i]]
data <- data_list[[i]]

mod_for_cast <- last_to_inits(mod_file)
mod_for_cast$nHostSpecies <- 1
mod_for_cast$nVectorSpecies <- 1
mod_for_cast <- setup_other_variables(mod_for_cast)
mod_for_cast <- forecast_spline_Lambda(mod_for_cast, 5, x_last = 1)
tt <- seq(0, ceiling(max(data$jdate) / 365) * 365 + (5 * 365), length.out = 200)

mod_for_cast <- xds_solve(mod_for_cast, Tmax = max(tt))

vals_for <- get_XH(mod_for_cast)
time_years <- mod_for_cast$outputs$time / 365 + FirstYear
t <- time_years

#base_mod <- model_list[[i]]  # Reset base model for each iteration
coverage <- c(0.3, 0.5, 0.8, 1)
par(mfrow = c(2, 2), mar = c(4, 4, 3, 1), oma = c(0, 0, 2, 0))

for (c in coverage) {
  itn_effect <- 0.9
  itn_start <- itn_effect*c
  itn_end <- 0.01
  decay_start <- 2023
  decay_end <- 2026
  t0 <- (decay_start + decay_end) / 2
  k <- 1.5

    effect_decay <- function(t, e0, e1, k_eff, t0_eff) {
    e1 + (e0 - e1) / (1 + exp(k_eff * (t - t0_eff)))
  }

cov_opts <- list(
  effect_decay(t, e0 = itn_start, e1 = itn_end, k_eff = k, t0_eff = t0)
)

coverage_func <- function(t) rep(c, length(t))
coverage_opts <- list(coverage_func(t))

 #mod_file <- setup_other_variables(mod_file)
#itn_mod1 <- last_to_inits(mod_file)
#itn_mod1$nHostSpecies <- 1
#itn_mod1$nVectorSpecies <- 1
#itn_mod1 <- setup_other_variables(itn_mod1)
itn_mod1 <- setup_bednets(
  mod_for_cast,
  coverage_name = "func",
  coverage_opts = coverage_opts,
  effectsizes_name = "func",
  effectsizes_opts = cov_opts
  )

#mod_for_cast_cov <- setup_other_variables(itn_mod1)
#mod_for_cast_cov <- forecast_spline_Lambda(itn_mod1, 5, x_last = 1)
mod_for_cast_cov <- xds_solve(itn_mod1, max(tt))
vals_cov <- get_XH(mod_for_cast_cov)

  df <- data.frame(
    Year = t,
    Original_PR = round(vals_for$true_pr,4),
    itn_PR = round(vals_cov$true_pr, 4)
  )
  df <- df[df$Year >= 2020,]

  plot(df$Year, df$Original_PR, type = "l", lwd = 2, col = "blue",
       ylim = c(0, 1), ylab = "Parasite Rate (PR)", xlab = "Year",
       main = paste(unique(data$district_name), "-", "cov=", c * 100, "%"))

  lines(df$Year, df$itn_PR, col = "darkred", lwd = 2)
  with(data, lines(jdate / 365 + FirstYear, pfpr, type = "o", col = "darkblue"))
}

}
```

```{r}
#pdf("itn_scenario_time_decay_cov.pdf")
#for(i in 1:length(itn_time))
for(i in 1:6)
  profile_itn(i, fitted_mod, data_list)
#dev.off(dev.cur())
```
