---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
attach(yaml::read_yaml("../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
# #load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
eir_files <- list.files(path = directory, pattern = "*_eir_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(eir_files[i])
}
```

 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){
  mod_file <- model_list[[i]]
  data <- data_list[[i]]

  #---------------------------------------------------------------------------------------------------
  #get indices from the tt in the trend corresponding to the value after the itn was given out.
  ix <- unique(sapply(itn_time[[i]], function(x) {
  idx <- which(fitted_mod[[i]]$EIRpar$trend_par$tt > x)
  if (length(idx) > 0) return(idx[1]) else return(NA)
}))
  ##--------------------------------------------------------------------------------------------------
  cf_max <- make_cf_base_max(ix, mod_file)
  cf_min <- make_cf_base_min(ix, mod_file)
  cf_median <- make_cf_base_median(ix, mod_file)
  cf_mean <- make_cf_base_mean(ix, mod_file)
  mod1a <- modify_baseline(mod_file, cf_max) 
  mod1b <- modify_baseline(mod_file, cf_min) 
  mod1c <- modify_baseline(mod_file, cf_median) 
  mod1d <- modify_baseline(mod_file, cf_mean) 
  vals <- get_XH(mod_file)
  vals1a <- get_XH(mod1a)
  vals1b <- get_XH(mod1b)
  vals1c <- get_XH(mod1c)
  vals1d <- get_XH(mod1d)

  with(vals1a, plot(time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred"))
  with(vals1b, lines(time/365+FirstYear, true_pr,  lwd=2, col="darkgreen"))
  with(vals1c, lines(time/365+FirstYear, true_pr, lwd=2,  col="purple4"))
  with(vals1d, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkorange"))
  with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data, lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  legend("topleft",  c("max", "min","median","mean"),  
  col = c("darkred", "darkgreen","purple4","darkorange"),
  lwd=2, pch=c(NA,NA,NA,NA,16), horiz = FALSE, bty="n")      
  add_itn_history(unique(data$district_name))

  ## -------------Effect Size--------------------------------------------------------------------------
  max_eff <- vals1a$true_pr
  min_eff <- vals1b$true_pr
  median_eff <- vals1c$true_pr
  mean_eff <- vals1d$true_pr
  base <- vals$true_pr

  max_effless <- max_eff[1:(length(max_eff) - 3)]/base
 
 min_effless <- min_eff[1:(length(min_eff)-3 )]/base
 median_effless <- median_eff[1:(length(median_eff)-3 )]/base
 mean_effless <- mean_eff[1:(length(mean_eff) - 3)]/base
 #----------------------------------------------------------------------------------------------------
 # computing itn _effect size for every three years
  t_time <- mod_file$outputs$time
  if (length(itn_time[[i]]) < 3) {
    return(NULL)  # Skip this district by returning NULL
  }

  itn_1 <- itn_time[[i]][length(itn_time[[i]]) - 2]
  itn_2 <- itn_time[[i]][length(itn_time[[i]]) - 1]
  itn_3 <- itn_time[[i]][length(itn_time[[i]])]
  
  closest_index1 <- which.min(abs(t_time - itn_1))
  closest_index2 <- which.min(abs(t_time - itn_2))
  closest_index3 <- which.min(abs(t_time - itn_3))


  
  # create a data frame for the effect sizes
  
  Effect_table <- data.frame(
  ITN_Type = c("ITN2","ITN3","ITN4" ),
  max_effect = round(c(mean(max_effless[closest_index1:closest_index2]), mean(max_effless[closest_index2:closest_index3]), mean(max_effless[closest_index3:length(t_time)])),2),
  min_effect = round(c(mean(min_effless[closest_index1:closest_index2]), mean(min_effless[closest_index3:closest_index3]), mean(min_effless[closest_index3:length(t_time)])),2),
  median_effect = round(c(mean(median_effless[closest_index1:closest_index2]), mean(median_effless[closest_index3:closest_index3]), mean(median_effless[closest_index3:length(t_time)])),2),
  mean_effect = round(c(mean(mean_effless[closest_index1:closest_index2]), mean(mean_effless[closest_index3:closest_index3]), mean(mean_effless[closest_index3:length(t_time)])),2),
  
  max_percent = round(c((1 - (1 / mean(max_effless[closest_index1:closest_index2]))) * 100, (1 - (1 / mean(max_effless[closest_index2:closest_index3]))) * 100, (1 - (1 / mean(max_effless[closest_index3:length(t_time)]))) * 100),2),
  min_percent = round(c((1 - (1 / mean(min_effless[closest_index1:closest_index2]))) * 100, (1 - (1 / mean(min_effless[closest_index2:closest_index3]))) * 100, (1 - (1 / mean(min_effless[closest_index3:length(t_time)]))) * 100),2),
  median_percent = round(c((1 - (1 / mean(median_effless[closest_index1:closest_index2]))) * 100, (1 - (1 / mean(median_effless[closest_index2:closest_index3]))) * 100, (1 - (1 / mean(median_effless[closest_index3:length(t_time)]))) * 100),2),
  mean_percent = round(c((1 - (1 / mean(mean_effless[closest_index1:closest_index2]))) * 100, (1 - (1 / mean(mean_effless[closest_index2:closest_index3]))) * 100, (1 - (1 / mean(mean_effless[closest_index3:length(t_time)]))) * 100),2))

  
  
  #-------------------------------------------------------------------------------------------------
  # ploting effect sizes
#    plot(mod_file$outputs$time/365+FirstYear,max_effless, type= "l",lwd= 2, col="darkred" , main=unique(data$district_name), xlab = "Time", ylab = "Effect Sizes", ylim = c(0, max(max_effless)) )
#   lines(mod_file$outputs$time/365+FirstYear,min_effless , lwd= 2, col="darkgreen")
#   lines(mod_file$outputs$time/365+FirstYear,median_effless, lwd= 2, col="purple4" )
#   lines(mod_file$outputs$time/365+FirstYear,mean_effless, lwd= 2, col="darkorange" )
#   
# #   legend("topleft",    #inset=-0.2 ,              # Position of the legend
# #   legend = c(
# #           paste0(
# #   "max_effs: ", sprintf("%.2f", mean(max_effless[closest_index3:length(t_time)], na.rm = TRUE)),
# #   " (", sprintf("%.2f%%", (1 - (1 / mean(max_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100)," reduction)")
# # ,
# # paste0("min_effs: ", sprintf("%.2f", mean(min_effless[closest_index3:length(t_time)], na.rm = TRUE)),
# #   " (", sprintf("%.2f%%", (1 - (1 / mean(min_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")")
# # ,
# # paste0("median_effs: ", sprintf("%.2f", mean(median_effless[closest_index3:length(t_time)], na.rm = TRUE)),
# #   " (", sprintf("%.2f%%", (1 - (1 / mean(median_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")"
# # ),
# #  paste0( "mean_effs: ", sprintf("%.2f", mean(mean_effless[closest_index3:length(t_time)], na.rm = TRUE)),
# #   " (", sprintf("%.2f%%", (1 - (1 / mean(mean_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")")),
# #   col = c("darkred", "darkgreen","purple4","darkorange"),
# #   lwd=2, pch=c(NA,NA,NA,NA,16), horiz = FALSE, bty="n") 
#   add_itn_history(unique(data$district_name))
return(data.frame(
      district_name = unique(data$district_name),
      Effect_table
      )
    )



  }

```

```{r}
#pdf("itn_districts.pdf")
for(i in 1)
  profile_itn(i, fitted_mod, data_list)
#dev.off(dev.cur())
```

```{r}
pdf("PBO_districts_cts_only.pdf")
malaria_itn_Effect <- list()
Royal_guard  <- c(75,145,106,123,2,94,92,11,142,1,105,77,117,110,111,6,33)
Permanent_dual <- c(8,35,10,60,44)
Interceptor <- c(146,118,128,26,114,23,46,24,61,57,134,131,133,45,72)
PBO <- setdiff(1:length(dist_name), c(Royal_guard,Permanent_dual,Interceptor))
for(i in Royal_guard) {
#for (i in setdiff(1:length(dist_name), c(10,27,33,35.37,42,86,95,98,99,101,140)))  {
  itn <- profile_itn(i, fitted_mod, data_list)  
  malaria_itn_Effect[[i]] <- itn  # Store each data.frame
}
dev.off()
# Combine all stored data.frames into one big data.frame
malaria_itn_eff <- do.call(rbind, malaria_itn_Effect)
# Save to CSV
write.csv(malaria_itn_eff, "../data/PBO_itn_eff.csv", row.names = FALSE)
```



