---
title: "Working with Models"
output: html_document
---

[`ramp.uganda`](../index.html)

***

load libraries 
This sets locations for `Box/RAMP` and `ramp.uganda` 
```{r}
library(ramp.xds)
library(dplyr)
library(ramp.uganda)
library(ramp.work)
library(ramp.control)
attach(yaml::read_yaml("../my_paths.yaml")) 
``` 

load district data from district dir
```{r,eval=F}
 #load("C:/Users/Admin/Documents/ramp.uganda/data/district_dir.rda")
load("C:/Users/doree/Documents/Github/ramp.uganda/data/district_dir.rda")
 dist_name <- sort(district_dir$district_name)
```



Get ITN timelines for all districts that recieved ITN and select only those values that are positive for Post-2015
```{r}
FirstYear <-2015
itn_time <- list()
for (j in dist_name) {
  dates <- get_itn_jdates(j, FirstYear)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    itn_time[[j]] <- sort(dates[dates > 0])
  } 
}
```


load files with fitted models from the box directory
```{r, eval=F}
directory <- paste(box_dir, "models", sep = "") 
eir_files <- list.files(path = directory, pattern = "*_eir_sis.rds", full.names = TRUE)
```


Get pfpr data by district 
```{r,eval=F}
data_list = list()
for(i in dist_name)
  data_list[[i]] <- get_district_pfpr(i)
```

Get fitted models to pfpr data for all the itn district
```{r, eval=F}
fitted_mod <- list()
for (i in 1:length(dist_name)) {
  fitted_mod[[i]] <- readRDS(eir_files[i])
  fitted_mod[[i]]$nHostSpecies <- 1
fitted_mod[[i]]$nVectorSpecies <- 1
}
```

 Profile for obtaining plots and effect sizes

```{r, fig.height=8, fig.width=11}
profile_itn = function(i, model_list, data_list){
  #mod_file <- model_list[[i]]
  mod_file <- fitted_mod[[1]]
  #data <- data_list[[i]]
  data <- data_list[[1]]

  #---------------------------------------------------------------------------------------------------
  #get indices from the tt in the trend corresponding to the value after the itn was given out.
  ix <- unique(sapply(itn_time[[i]], function(x) {
  idx <- which(fitted_mod[[i]]$EIRpar$trend_par$tt > x)
  if (length(idx) > 0) return(idx[1]) else return(NA)
}))
  ##--------------------------------------------------------------------------------------------------
  cf_max <- make_cf_base_max(ix, mod_file)
  cf_min <- make_cf_base_min(ix, mod_file)
  cf_median <- make_cf_base_median(ix, mod_file)
  cf_mean <- make_cf_base_mean(ix, mod_file)
  mod1a <- modify_baseline(mod_file, cf_max) 
  mod1b <- modify_baseline(mod_file, cf_min) 
  mod1c <- modify_baseline(mod_file, cf_median) 
  mod1d <- modify_baseline(mod_file, cf_mean) 
  vals <- get_XH(mod_file)
  vals1a <- get_XH(mod1a)
  vals1b <- get_XH(mod1b)
  vals1c <- get_XH(mod1c)
  vals1d <- get_XH(mod1d)

 # plot(vals1a$time/365+FirstYear, vals1a$true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred")
 # lines(vals1b$time/365+FirstYear, vals1b$true_pr,lwd=2, col="darkgreen")
# lines(vals1c$time/365+FirstYear, vals1c$true_pr,lwd=2, col="darkorange")
# lines(vals1d$time/365+FirstYear, vals1d$true_pr,lwd=2, col="darkblue")
# lines(vals$time/365+FirstYear, vals$true_pr,lwd=2, col="purple4")
# lines(data$jdate/365+FirstYear, data$pfpr,pch=16,type = "o", col="purple4")
  
  with(vals1a, plot(time/365+FirstYear, true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred"))
  with(vals1b, lines(time/365+FirstYear, true_pr,  lwd=2, col="darkgreen"))
  with(vals1c, lines(time/365+FirstYear, true_pr, lwd=2,  col="purple4"))
  with(vals1d, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkorange"))
  with(vals, lines(time/365+FirstYear, true_pr, lwd=2,  col="darkblue"))
  with(data, lines(jdate/365+FirstYear, pfpr, pch=16,type = "o", col="darkblue"))
  legend("topleft",  c("max baseline", "min baseline","median baseline","mean baseline"),  
  col = c("darkred", "darkgreen","purple4","darkorange"),
  lwd=2, pch=c(NA,NA,NA,NA,16), horiz = FALSE, bty="n")      
  add_itn_history(unique(data$district_name))
  add_irs_history(unique(data$district_name))
  
  ######.........using the models without knowledge of what happened before..................
   mod_for_cast <- last_to_inits(mod_file)
   mod_for_casta <- last_to_inits(mod1a)
   mod_for_castb <- last_to_inits(mod1b)
   mod_for_castc <- last_to_inits(mod1c)
   mod_for_castd <- last_to_inits(mod1d)
  #mod_for_cast<- forecast_spline_EIR(mod_for_cast, 5,x_last=1)
#  tt1<- seq((ceiling(max(data$jdate)/365)*365)-(365*2),ceiling(max(data$jdate)/365)*365+(5*365), length.out=200)
  tt <- seq(ceiling(max(data$jdate)/365)*365, ceiling(max(data$jdate)/365)*365+(5*365), length.out=200)
  #tt <-  seq(0, (10*365),length.out=200)
  
  mod_for_cast <- xds_solve_cohort(mod_for_cast, times=tt)
  mod_for_casta <- xds_solve_cohort(mod_for_casta, times=tt)
  mod_for_castb <- xds_solve_cohort(mod_for_castb, times=tt)
  mod_for_castc <- xds_solve_cohort(mod_for_castc, times=tt)
  mod_for_castd <- xds_solve_cohort(mod_for_castd, times=tt)
  
  vals_forcast <- get_XH(mod_for_cast)
  vals_forcasta <- get_XH(mod_for_casta)
  vals_forcastb <- get_XH(mod_for_castb)
  vals_forcastc <- get_XH(mod_for_castc)
  vals_forcastd <- get_XH(mod_for_castd)
  
  #plot(vals_forcast$time/365+FirstYear, vals_forcast$true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred")
  #lines(vals_forcasta$time/365+FirstYear, vals_forcasta$true_pr,lwd=2, col="darkgreen")
#lines(vals_forcastb$time/365+FirstYear, vals_forcastb$true_pr,lwd=2, col="darkblue")
#lines(vals_forcastc$time/365+FirstYear, vals_forcastc$true_pr,lwd=2, col="darkorange")
#lines(vals_forcastd$time/365+FirstYear, vals_forcastd$true_pr,lwd=2, col="purple4")
  
  
 ######.........using the models with knowledge of what happened before.................. 
  mod_for_castf <- forecast_spline_EIR(mod_for_cast, 5,x_last=8)
  mod_for_castfa <- forecast_spline_EIR(mod_for_casta, 5,x_last=8)
  mod_for_castfb <- forecast_spline_EIR(mod_for_castb, 5,x_last=8)
  mod_for_castfc <- forecast_spline_EIR(mod_for_castc, 5,x_last=8)
  mod_for_castfd <- forecast_spline_EIR(mod_for_castd, 5,x_last=8)
  
  
  tt <- seq(0,ceiling(max(data$jdate)/365)*365+(5*365) ,length.out=200)
  #tt <- seq(ceiling(max(data$jdate)/365)*365, ceiling(max(data$jdate)/365)*365+(5*365), length.out=200)
  mod_for_castf <- xds_solve_cohort(mod_for_castf, times=tt)
  mod_for_castfa <- xds_solve_cohort(mod_for_castfa, times=tt)
  mod_for_castfb <- xds_solve_cohort(mod_for_castfb, times=tt)
  mod_for_castfc <- xds_solve_cohort(mod_for_castfc, times=tt)
  mod_for_castfd <- xds_solve_cohort(mod_for_castfd, times=tt)
  
  
  vals_forcastf <- get_XH(mod_for_castf)
  vals_forcastfa <- get_XH(mod_for_castfa)
  vals_forcastfb <- get_XH(mod_for_castfb)
  vals_forcastfc <- get_XH(mod_for_castfc)
  vals_forcastfd <- get_XH(mod_for_castfd)
  
  #plot(vals_forcastf$time/365+FirstYear, vals_forcastf$true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred")
  #lines(vals_forcastfa$time/365+FirstYear, vals_forcastfa$true_pr,lwd=2, col="darkgreen")
#lines(vals_forcastfb$time/365+FirstYear, vals_forcastfb$true_pr,lwd=2, col="darkblue")
#lines(vals_forcastfc$time/365+FirstYear, vals_forcastfc$true_pr,lwd=2, col="darkorange")
#lines(vals_forcastfd$time/365+FirstYear, vals_forcastfd$true_pr,lwd=2, col="purple4")
 

  
##################........running the forecast at the end of the data......................######################..
  
  tt1 <- seq(ceiling(max(data$jdate)/365)*365, ceiling(max(data$jdate)/365)*365+(5*365), length.out=200)
  mod_for_castf1 <- xds_solve_cohort(mod_for_castf, times=tt1)
  mod_for_castf1a <- xds_solve_cohort(mod_for_castfa, times=tt1)
  mod_for_castf1b <- xds_solve_cohort(mod_for_castfb, times=tt1)
  mod_for_castf1c <- xds_solve_cohort(mod_for_castfc, times=tt1)
  mod_for_castf1d <- xds_solve_cohort(mod_for_castfd, times=tt1)
  
  
  vals_forcastf1 <- get_XH(mod_for_castf1)
  vals_forcastf1a <- get_XH(mod_for_castf1a)
  vals_forcastf1b <- get_XH(mod_for_castf1b)
  vals_forcastf1c <- get_XH(mod_for_castf1c)
  vals_forcastf1d <- get_XH(mod_for_castf1d)
  
  
  #plot(vals_forcastf1$time/365+FirstYear, vals_forcastf1$true_pr, ylab = "PR",lwd=2, xlab = "Time", main=unique(data$district_name), type = "l", ylim = c(0,1), col="darkred")
  #lines(vals_forcastf1a$time/365+FirstYear, vals_forcastf1a$true_pr,lwd=2, col="darkgreen")
#lines(vals_forcastf1b$time/365+FirstYear, vals_forcastf1b$true_pr,lwd=2, col="darkblue")
#lines(vals_forcastf1c$time/365+FirstYear, vals_forcastf1c$true_pr,lwd=2, col="darkorange")
#lines(vals_forcastf1d$time/365+FirstYear, vals_forcastf1d$true_pr,lwd=2, col="purple4")
  
 #########................. Can you forecast 
  
  ## -------------Effect Size--------------------------------------------------------------------------
  max_eff <- vals1a$true_pr
  min_eff <- vals1b$true_pr
  median_eff <- vals1c$true_pr
  mean_eff <- vals1d$true_pr
  base <- vals$true_pr
 
 
   max_effless <- max_eff[1:(length(max_eff) - 3)]/base
 
 min_effless <- min_eff[1:(length(min_eff)-3 )]/base
 median_effless <- median_eff[1:(length(median_eff)-3 )]/base
 mean_effless <- mean_eff[1:(length(mean_eff) - 3)]/base
 #----------------------------------------------------------------------------------------------------
 # computing itn _effect size for every three years
  t_time <- mod_file$outputs$time
  itn_3 <- itn_time[[i]][length(itn_time[[i]])]
  closest_index3 <- which.min(abs(t_time - itn_3))


  
  # create a data frame for the effect sizes
  
  Effect_table <- data.frame(
  ITN_Type = c("Royal Guard" ),
  max_effect = round(c( mean(max_effless[closest_index3:length(t_time)])),2),
  min_effect = round(c( mean(min_effless[closest_index3:length(t_time)])),2),
  median_effect = round(c(mean(median_effless[closest_index3:length(t_time)])),2),
  mean_effect = round(c( mean(mean_effless[closest_index3:length(t_time)])),2),
  
  max_percent = round(c((1 - (1 / mean(max_effless[closest_index3:length(t_time)]))) * 100),2),
  min_percent = round(c((1 - (1 / mean(min_effless[closest_index3:length(t_time)]))) * 100),2),
  median_percent = round(c((1 - (1 / mean(median_effless[closest_index3:length(t_time)]))) * 100),2),
  mean_percent = round(c( (1 - (1 / mean(mean_effless[closest_index3:length(t_time)]))) * 100),2),
  
  max_base = round(c( mean(max_eff[closest_index3:length(t_time)])),2),
  min_base = round(c( mean(min_eff[closest_index3:length(t_time)])),2),
  median_base = round(c(mean(median_eff[closest_index3:length(t_time)])),2),
  mean_base = round(c( mean(mean_eff[closest_index3:length(t_time)])),2))
  
  #-------------------------------------------------------------------------------------------------
  # ploting effect sizes
   plot(mod_file$outputs$time/365+FirstYear,max_effless, type= "l",lwd= 2, col="darkred" , main=unique(data$district_name), xlab = "Time", ylab = "Effect Sizes", ylim = c(0, max(max_effless)) )
  lines(mod_file$outputs$time/365+FirstYear,min_effless , lwd= 2, col="darkgreen")
  lines(mod_file$outputs$time/365+FirstYear,median_effless, lwd= 2, col="purple4" )
  lines(mod_file$outputs$time/365+FirstYear,mean_effless, lwd= 2, col="darkorange" )

  legend("topleft",    #inset=-0.2 ,              # Position of the legend
  legend = c(
          paste0(
  "max_effs: ", sprintf("%.2f", mean(max_effless[closest_index3:length(t_time)], na.rm = TRUE)),
  " (", sprintf("%.2f%%", (1 - (1 / mean(max_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100)," reduction)")
,
paste0("min_effs: ", sprintf("%.2f", mean(min_effless[closest_index3:length(t_time)], na.rm = TRUE)),
  " (", sprintf("%.2f%%", (1 - (1 / mean(min_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")")
,
paste0("median_effs: ", sprintf("%.2f", mean(median_effless[closest_index3:length(t_time)], na.rm = TRUE)),
  " (", sprintf("%.2f%%", (1 - (1 / mean(median_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")"
),
 paste0( "mean_effs: ", sprintf("%.2f", mean(mean_effless[closest_index3:length(t_time)], na.rm = TRUE)),
  " (", sprintf("%.2f%%", (1 - (1 / mean(mean_effless[closest_index3:length(t_time)], na.rm = TRUE))) * 100),")")),
  col = c("darkred", "darkgreen","purple4","darkorange"),
  lwd=2, pch=c(NA,NA,NA,NA,16), horiz = FALSE, bty="n")
  add_itn_history(unique(data$district_name))
  add_irs_history(unique(data$district_name))
return(data.frame(
      district_name = unique(data$district_name),
      Effect_table
      )
    )



  }

```

```{r}
#pdf("itn_districts.pdf")
for(i in 1)
  profile_itn(i, fitted_mod, data_list)
#dev.off(dev.cur())
```

```{r}
#pdf("all_districts_2023_type.pdf")
malaria_itn_Effect <- list()
Royal_guard  <- c(75,145,106,123,2,94,92,11,142,1,105,77,117,110,111,6,33)
Permanent_dual <- c(8,10,60,35,44)
Interceptor <- c(146,118,128,26,114,23,46,24,61,57,134,131,133,45,72)
#cities <- c(10,33,35,37,42,86,95,99,101,140,98,27)
 PBO <- setdiff(1:length(dist_name), c(Royal_guard,Permanent_dual,Interceptor))

for (i in Royal_guard) {
#for (i in setdiff(1:length(dist_name), c(10,27,33,35.37,42,86,95,98,99,101,140)))  {
  itn <- profile_itn(i, fitted_mod, data_list)  
  malaria_itn_Effect[[i]] <- itn  # Store each data.frame
}
#dev.off()
# Combine all stored data.frames into one big data.frame
malaria_itn_eff <- do.call(rbind, malaria_itn_Effect)
# Save to CSV
write.csv(malaria_itn_eff, "../data/ITN/ITN_2023/district_2023_itn_eff_royal.csv", row.names = FALSE)
```



```{r}
files1 <- list.files(path = "../data/ITN/ITN_2023", pattern = "*.csv", full.names = TRUE)
combined_data <- do.call(rbind, lapply(files1, read.csv))
write.csv(combined_data, "../data/ITN/ITN_2023/merged_itn_eff.csv", row.names = FALSE)
```

```{r}
FirstYear <-2015
irs_time_full <- list()
no_irs <- c()

for (j in dist_name) {
  dates <- get_irs_jdates(j, 2023)

  if (!is.null(dates) && length(dates) > 0 && any(dates > 0)) {
    irs_time_full[[j]] <- sort(dates[dates > 0])
  } else {
    no_irs <- c(no_irs, j)
  }
}
irs_time <-  irs_time_full

irs_dist <- list()
for (i in 1:length(irs_time))
  irs_dist[[i]]<- names(irs_time)[i]

#irs_dist <- irs_dist_full[-c(4, 7,8,9,10,11,13,14,15,25,31,34)]
irs_dist <- irs_dist[!sapply(irs_dist, is.na)]
```

```{r}
dist_itn_data <- read.csv(file="../data/ITN/ITN_2023/merged_itn_eff.csv")
dist_itn_data$IRS_status <- ifelse(dist_itn_data$district %in% irs_dist, "IRS", "No IRS")
write.csv(dist_itn_data, "../data/ITN/ITN_2023/updated_itn_eff.csv", row.names = FALSE)
```



```{r}
library(ggplot2)
itn_irs_data <- read.csv(file="../data/ITN/ITN_2023/updated_itn_eff.csv")
ggplot(itn_irs_data, aes(x = mean_base, y = mean_percent, color = ITN_Type, shape = IRS_status)) +
  geom_point(size = 2) +
  #geom_hline(yintercept = 1, linetype = "dashed", color = "darkred") +  # Horizontal line at y = 1
  geom_hline(yintercept = 0, linetype = "solid", color = "gray") +    # Horizontal line at y = 0
  geom_vline(xintercept = 0, linetype = "solid", color = "darkred") +    # Vertical line at x = 0
  scale_color_manual(values = c("PBO" = "darkblue", "Royal Guard" = "red", "Interceptor" = "green", "Permanent Dual" = "purple")) +  
  scale_shape_manual(values = c("IRS" = 17, "No IRS" = 16)) +  
  labs(title = "Effect sizes  of ITN by District and IRS status",
       x = "Average Baseline",
       y = "Effect size",
       color = "ITN type",
       shape = "IRS Districts") +
  theme_minimal()
```
```{r}
itn_irs_data <- read.csv(file="../data/ITN/ITN_2023/updated_itn_eff.csv")
ggplot(itn_irs_data, aes(x = mean_base, y = mean_percent, color = ITN_Type, shape = IRS_status)) +
  geom_point(size = 2) +
  #geom_hline(yintercept = 1, linetype = "dashed", color = "darkred") +  # Reference line at y = 1
  geom_hline(yintercept = 0, linetype = "solid", color = "darkred") +      # Reference line at y = 0
  geom_vline(xintercept = 0, linetype = "solid", color = "darkred") +      # Reference line at x = 0
  scale_color_manual(values = c(
    "PBO" = "darkblue",
    "Royal Guard" = "red",
    "Interceptor" = "green",
    "Permanent Dual" = "purple"
  )) +  
  scale_shape_manual(values = c("IRS" = 17, "No IRS" = 16)) +  
  facet_wrap(~ ITN_Type) +  # Creates a separate panel for each ITN type
  labs(
    title = "Effect sizes of ITN by District and IRS Status",
    x = "Average Baseline",
    y = "Effect Size",
    color = "ITN Type",
    shape = "IRS Districts"
  ) +
  theme_minimal()

```
```{r}
itn_irs_data <- read.csv(file="../data/ITN/ITN_2023/updated_itn_eff.csv")
ggplot(itn_irs_data, aes(x = mean_base, y = mean_effect, color = ITN_Type)) +
  geom_point(aes(shape = IRS_status), size = 2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "darkred") +
  geom_hline(yintercept = 0, linetype = "solid", color = "gray") +
  geom_vline(xintercept = 0, linetype = "solid", color = "gray") +
  scale_color_manual(values = c(
    "PBO" = "darkblue",
    "Royal Guard" = "red",
    "Interceptor" = "green",
    "Permanent Dual" = "purple"
  )) +
  scale_shape_manual(values = c("IRS" = 17, "No IRS" = 16)) +
  labs(title = "Effect sizes of ITN by District and IRS status",
       x = "Average Baseline",
       y = "Effect size",
       color = "ITN Type",
       shape = "IRS Status") +
  facet_grid(IRS_status ~ ITN_Type) +  # Separate by both variables
  theme_minimal()

```
```{r}
itn_irs_data <- read.csv(file="../data/ITN/ITN_2023/updated_itn_eff.csv")
ggplot(itn_irs_data, aes(x = mean_base, y = mean_effect, color = ITN_Type)) +
  geom_point(aes(shape = IRS_status), size = 2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "darkred") +  # y = 1 reference
  geom_hline(yintercept = 0, linetype = "solid", color = "gray") +      # y = 0 baseline
  geom_vline(xintercept = 0, linetype = "solid", color = "gray") +      # x = 0 baseline
  scale_color_manual(values = c("PBO" = "darkblue", 
                                "Royal Guard" = "red", 
                                "Interceptor" = "green", 
                                "Permanent Dual" = "purple")) +
  scale_shape_manual(values = c("IRS" = 17, "No IRS" = 16)) +
  facet_grid(ITN_Type ~ IRS_status) +  # Facet by ITN type and IRS status
  labs(title = "Effect Sizes of ITN by ITN Type and IRS Status",
       x = "Average Baseline",
       y = "Effect Size",
       color = "ITN Type",
       shape = "IRS Status") +
  theme_minimal()

```

```{r}
itn_irs_data <- read.csv(file="../data/ITN/ITN_2023/updated_itn_eff.csv")
ggplot(itn_irs_data, aes(x = mean_base, y = mean_percent, color = ITN_Type)) +
  geom_point(aes(shape = IRS_status), size = 2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "darkred") +
  geom_hline(yintercept = 0, linetype = "solid", color = "gray") +
  geom_vline(xintercept = 0, linetype = "solid", color = "gray") +
  scale_color_manual(values = c("PBO" = "darkblue", 
                                "Royal Guard" = "red", 
                                "Interceptor" = "green", 
                                "Permanent Dual" = "purple")) +
  scale_shape_manual(values = c("IRS" = 17, "No IRS" = 16)) +
  facet_wrap(~ ITN_Type + IRS_status) +
  labs(title = "Effect Sizes of ITNs by Type and IRS Status",
       x = "Average Baseline",
       y = "Effect Size",
       color = "ITN Type",
       shape = "IRS Status") +
  theme_minimal()

```

